\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{\Large{Ritwik Bhaduri}} \\
\indent 61/18 Jorabagan road, \\
\indent Kolkata, West Bengal, India - 700047\\
\indent Email-id : \textbf{ritwik.bhaduri@gmail.com} \\
\indent Mobile No.: \textbf{7687853608} \\
\indent Alt Mob No.: \textbf{9434233190} \\

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
\hline
\textbf{Examination} & \textbf{Institute} & \textbf{Year} & \textbf{Percentage/\%} \\
\hline
Bachelor of Statistics(Honours) II year Fourth semester\,\, & \textit{Indian Statistical Institute} & 2017-18 & 86.8 \\
Bachelor of Statistics(Honours) II year Third semester\,\, & \textit{Indian Statistical Institute} & 2017-18 & 81.6 \\
Bachelor of Statistics(Honours) I year Second semester\,\, & \textit{Indian Statistical Institute} & 2016-17 & 87 \\
Bachelor of Statistics(Honours) I year First semester\,\, & \textit{Indian Statistical Institute} & 2016-17 & 89.25 \\
Class XII (WBCHSE)  & \textit{R.K. mission, Narendrapur} & 2016 & 93.8 \\
Class X (WBBSE) & \textit{R.K. mission, Narendrapur} & 2014 & 93.57\\
\hline
\end{tabular}
%\end{center}
%\end{table}
\\ \\

\resheading{\textbf{AWARDS AND ACHIVEMENTS} }\\[\lsep]
\begin{itemize}
\item \noindent JEE Main Rank - 2714.
\item \noindent Selected for IIT by clearing JEE advanced
\item \noindent KVPY rank 481.
\item \noindent Selected for Chennai Mathematical Institute, BSc Computer Science and Mathematics.
\item \noindent Recipient of KVPY fellowship
\item \noindent Eligible for INSPIRE programme by Department of Science and Technology India
\item \noindent Awarded prize money for meritorious performance in first year.
\item \noindent Selected for JBNSTS camp, organized by DST-Inspire.
\end{itemize}

\resheading{\textbf{FIELDS OF INTEREST} }\\[\lsep]
\begin{itemize}
\item \noindent Probability, Markov chain, Applied Statistics, Machine learning
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Languages} : C, Python, R 
\item \noindent \textbf{Tools} (\LaTeX, Rstudio, MS Office (MS Excel, MS Word, MS Powerpoint) ).
\end{itemize}

\resheading{\textbf{MAJOR PROJECTS AND SEMINAR} }\\[\lsep]
\begin{itemize}
\item \textbf{An urn model and the odds ratio-based design
for clinical trials} (Ongoing Group Project) \\
 \emph{(Guide:Gopal K. Basak, August'18 - till date)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective : To provide a theoretical justification of using odds ratio based adaptive allocation design of clinical trials.
	\item The idea here is that while trying to establish which of the two treatments is in fact better, we would like to allocate more patients to a statistically better treatment during the trial itself, thus addressing the trade-off between the efficient estimation and more ethical treatment of the participants.

	\item Studied various topics like Markov chain Monte-Carlo, Urn models etc and some papers related to the topic.
    \end{itemize}

\item \textbf{Unsupervised learning - K means, Image clustering using K means.
} (2nd Year summer project) \\
 \emph{(Guide: Prof. Swagatam Das
, May'18 - July'18)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective 1 : To study various variations of standard k means and arrive at theoretical results for their convergence (Expressing K means as a gradient descent algorithm and commenting on the convergence rates).
	\item Objective 2 : Clustering the colours in an image and representing an image with minimal number of colours reducing image size without affecting the quality of the image.
	\item Implementation of k means and other algorithms in R and Python.
	\end{itemize}

\item \textbf{Summer Internship in Cryptology }
(1st Year summer Internship) \\
 \emph{(R. C. Bose Centre for Cryptology and Security
, May'17 - July'17)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective : To study different aspects of cryptography and statistical cryptanalysis, learning various public key and private key cryptography, stream and block ciphers etc.
	\item Implementation of stream and block ciphers in python and C. 
	\end{itemize}

\item \textbf{Analysis of RC4 streamcipher }
(1st Year summer project) \\
 \emph{(Prof. Gutam K. Paul
, May'17 - July'17)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective : To attack the RC4 streamcipher using bias in the initial bits of output and perform related key cryptanalysis .
	\item Implemenation of RC4 in python and demonstrating the bias in the initial output . 
	\end{itemize}
	
\item \textbf{Class projects (Statistics) }
 \\
 \emph{Prof. Smarajit Bose
, July'16 - April'17)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item 1) Studying correlation between prices of house and tax payment using simple linear regression in R.
	\item 2) Studying the effects of natural and artificial factors on climate using Multiple linear regression and Anova in R. 
	\item 3) Fitting real data to discrete and continuous distributions ( Poisson, Normal and Gamma ) and commenting on the goodness of fit using Pearson's Chi square, P value in R.
	\end{itemize}
\end{itemize}

\resheading{\textbf{COURSES} }\\[\lsep]
\begin{itemize}
\item Statistical Methods
\item Probability theory
\item Stochastic processes and Markov chain
\item Parametric Inference (ongoing)
\item Linear Models
\item Economics
\item Analysis, Linear Algebra, Abstract Algebra, Differential Equation and Discrete Maths.
\item Sample Survey (ongoing)
\item C programming and Design and analysis of algorithms (ongoing)
\end{itemize}

\resheading{\textbf{ONLINE COURSES} }\\[\lsep]
\begin{itemize}
\item \textbf{Cryptography 1 } 
by Prof. Dan Boneh\\
Online course offered by \textbf{Stanford University} on Coursera. 
\end{itemize}

\resheading{\textbf{STRENGTHS} }\\[\lsep]
\begin{itemize}
\item \noindent Positive Attitude, Hardworking, Inquisitive, Commitment.
\end{itemize}

\resheading{\textbf{INTEREST AND HOBBIES} }\\[\lsep]
\begin{itemize}
\item \noindent Watching movies, Music, Trekking and Hiking, playing badminton, football etc.
\end{itemize}

\resheading{\textbf{POSITION OF RESPONSIBILITIES} }\\[\lsep]
\begin{itemize}
\item \noindent Event head of short film competition - Montage in college fest from 2017 till date.
\end{itemize}

\end{document}

